### 2024-12-09 Draft1.tex
Finished decryption section

To decrypt \( M \), the recipient solves the differential equation with the transmitted function \( y(x) \) and initial conditions.

\subsubsection*{Step 1: Verify the Initial Conditions}

Using the transmitted equation and encrypted function:
\begin{enumerate}
    \item Compute \( y(0) \):
    \[
    y(0) = -10237.5e^0 - 23887.5e^0 + 34125 = 0.
    \]

    \item Compute \( y'(0) \):
    \[
    y'(x) = -20475e^{2x} - 71662.5e^{3x} + 45678 - 60904x + 45678x^2,
    \]
    \[
    y'(0) = -20475 - 71662.5 + 45678 = 45678.
    \]
\end{enumerate}

Both initial conditions match the transmitted values, confirming the solution's integrity.

After transmission and decryption, the recipient is able to correctly calculate \( M \) directly from the initial condition \( y'(0) = M \). As a result, \( y'(0) = M = 45678 \).

>>>>

To decrypt \( M \), the recipient must solve the differential equation:
\[
\frac{d^2y}{dx^2} - 5\frac{dy}{dx} + 6y = f(x),
\]
using the transmitted encrypted function \( y(x) \), the initial conditions, and the forcing function which they had before transmission \( f(x) = 45678x^2 + 34125 \).

To begin, the recipient verifies the initial conditions to confirm the integrity of the transmitted function.

\centering First, compute \( y(0) \). Substitute \( x = 0 \) into the transmitted \( y(x) \):
\[
y(0) = C_1e^{2(0)} + C_2e^{3(0)} + 13723.44 = C_1 + C_2 + 13723.44.
\]
Using the initial condition \( y(0) = M = 83495 \), solve for \( C_1 + C_2 \):
\[
C_1 + C_2 = M - 13723.44 = 83495 - 13723.44 = 69771.56.
\]

Next, compute \( y'(0) \). Differentiate \( y(x) \) to find:
\[
y'(x) = 2C_1e^{2x} + 3C_2e^{3x} + 2(7613)x + 12688.33.
\]
Substitute \( x = 0 \):
\[
y'(0) = 2C_1 + 3C_2 + 12688.33.
\]
Using the initial condition \( y'(0) = 0 \), solve for \( 2C_1 + 3C_2 \):
\[
2C_1 + 3C_2 + 12688.33 = 0 \quad \Rightarrow \quad 2C_1 + 3C_2 = -12688.33.
\]

With the two equations:
\[
C_1 + C_2 = 69771.56,
\]
\[
2C_1 + 3C_2 = -12688.33,
\]
solve for \( C_1 \) and \( C_2 \). From the first equation, express \( C_1 \) in terms of \( C_2 \):
\[
C_1 = 69771.56 - C_2.
\]
Substitute \( C_1 = 69771.56 - C_2 \) into the second equation:
\[
2(69771.56 - C_2) + 3C_2 = -12688.33.
\]
Simplify:
\[
139543.12 - 2C_2 + 3C_2 = -12688.33 \quad \Rightarrow \quad 139543.12 + C_2 = -12688.33.
\]
Solve for \( C_2 \):
\[
C_2 = -12688.33 - 139543.12 = -152231.45.
\]
Substitute \( C_2 = -152231.45 \) back into \( C_1 = 69771.56 - C_2 \):
\[
C_1 = 69771.56 - (-152231.45) = 69771.56 + 152231.45 = 222003.01.
\]

Thus, the values of the constants are:
\[
C_1 = 222003.01, \quad C_2 = -152231.45.
\]

Finally, verify \( M \) using the transmitted initial condition \( y(0) \):
\[
y(0) = C_1 + C_2 + 13723.44 = 222003.01 - 152231.45 + 13723.44 = 83495.
\]
This confirms that the recipient has correctly decrypted \( M = 83495 \).
